Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-06 ms/manuscript.Rmd
Add t-value to CWMs

**\fig \@ref(fig:cwm-div)**: Change in selected functional traits of ferns on Moorea, French Polynesia across environmental gradients and between growth habit types (epiphytic or terrestrial). Epiphytic values in green, terrestrial values in brown. Scatterplots show community-weighted mean (CWM) values for each trait plotted against either minimum relative humidity ($\n = 13$ communities each for epiphytes and terrestrial species) or elevation ($\n = 17$ communities each). Trendlines indicate significant relationships determined by a linear model at $\pval<0.05$. Boxplots show median values (bold lines) by growth habit (epiphytic or terrestrial) across all communities (epiphytic communities, $\n = 17$; terrestrial communities, $\n = 17$). Lower and upper hinges correspond to first and third quartiles, and whiskers extend to values within 1.5 $\times$ the interquartile range. Asterisks indicate statistical significance of two-sided \tval-test for differences between epiphytic and terrestrial species; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$. Trends for three leaf size traits (stipe length, frond length, and frond with) were quantitatively very similar, so of these we only present stipe length.

**\fig \@ref(fig:comm-div)**: Functional and phylogenetic diversity of epiphytic and terrestrial fern communities along an elevational gradient on Moorea, French Polynesia. Epiphytic communities in green, terrestrial communities in brown. Response variable abbreviations as follows: MPD~phy~, standard effect size (SES) of mean phylogenetic distance; MNTD~phy~, SES of mean nearest taxon distance; MPD~func~, SES of mean functional distance; MNTD~func~, SES of mean nearest functional distance. Trendlines indicate significant relationships determined by a linear model at $\pval<0.05$. Boxplots show median values (bold lines) of response variables by growth habit (epiphytic or terrestrial). Hinges and whiskers as in \fig \@ref(fig:cwm-div). Asterisks indicate statistical significance of one-sided \tval-test; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.

>>>>

**\fig \@ref(fig:cwm-div)**: Change in community-weighted mean (CWM) values of epiphytic and terrestrial fern communities along an elevational gradient on Moorea, French Polynesia. Epiphytic communities in green, terrestrial communities in brown. Error bars are community-weighted standard deviation (values below zero not shown). Trendlines and \rval^2^ shown for significant relationships with elevation or the interaction of elevation and growth habit as determined by a linear model at $\pval<0.05$. \tval shown for significant differences between means of CWMs by growth habit as determined by a two-sided \tval-test at $\pval<0.05$; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.

**\fig \@ref(fig:comm-div)**: Functional and phylogenetic diversity of epiphytic and terrestrial fern communities along an elevational gradient on Moorea, French Polynesia. Epiphytic communities in green, terrestrial communities in brown. Response variable abbreviations as follows: MPD~phy~, standard effect size (SES) of mean phylogenetic distance; MNTD~phy~, SES of mean nearest taxon distance; MPD~func~, SES of mean functional distance; MNTD~func~, SES of mean nearest functional distance. Trendlines indicate significant relationships as determined by a linear model at $\pval<0.05$. Boxplots show median values (bold lines) by growth habit. Lower and upper hinges correspond to first and third quartiles, and whiskers extend to values within 1.5 $\times$ the interquartile range. Asterisks indicate statistical significance of two-sided \tval-test; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.
